\section{Related Work}
To my knowledge, no work has been done in relation to a system of this type. Work has been done in decentralized multi-agent path planning. However, the standard for robot navigation is for the ground robots to calculate the paths themselves such as in \cite{DeadlockDigani}, \cite{DeadlockDraganjac}, \cite{FTC-A}, and \cite{DecentralizedPlanningVelagapudi}. Performing planning directly on the robots puts a heavy load on the robot and requires that they be equipped with unnecessarily powerful hardware. Further work has been done to reduce this load on the robots by employing hierarchical graphs which are used to perform path planning algorithms such as \cite{FTC-A} and \cite{CTF-A}. 

The previous work is primarily designed for a static environment. For dynamic environments, Simultaneous Localization and Mapping (SLAM) \cite{SLAM}, can be used. In this case, the robots are required to create the region's map locally. Unfortunately this means that before point-to-point planned navigation can take place, the area must be fully explored. While it is suited for dynamic environments, it is unaware of changes in the environment until the region is revisited by the robot. Further work has been done to allow this method to be both decentralized and distributed \cite{DecentralizedSLAM}.

For these multi-agent systems, work has also been done in avoiding deadlock. In \cite{DeadlockDigani}, the authors present a method based on resource allocation. This method requires robots to communicate as they approach an "intersection" to determine who the intersection is allocated to. In \cite{DeadlockDraganjac}, robots are given a "private zone" that is maintained as they navigate. If deadlock arises, one robot may move to a clear area in its private zone allowing the other robot to pass. In \cite{DecentralizedPlanningVelagapudi}, the authors make clever use of the birthday problem. A robot $r$ will share its path with a random set of robots $R_s$, a subset of all robots $R$. Each robot then builds a lookup table of its own path and those shared with it. Using this, there is a high probability that a pair of paths causing deadlock will be detected.